Seismic parameter estimation and the Canadian crust

### 2013-08-08 paper/draftBP.tex
crust1

\item Quiet zone in discontinuity data

\item Compare data to Crust 2.0. What do the differences mean.
  \begin{itemize}
  \item Lith 5.0 data?
  \end{itemize}

@@

\item Secular variation in NE Churchill from thinner crusts to thicker as we move East
  \begin{itemize}
  \item in the literature? See Lith 5.0: A revised crustal model for Canada based on lithoprobe results.
  \end{itemize}

 \item Explanation of results

 \item Canada H and Vp/Vs

 \item Lith5.0 (Perry, 2002) estimates for Canadian crustal averages is 38 km. The Crust
   2.0 average is 38 km as well, however this is expected since Crust2.0 data for
   Canada is based on the same data as that of Lith5.0 .... is it definately?

 \item Make some comparison to global average?

>>>>

\item Crustal discontinuities
  \begin{itemize}
    \item No observed reflector patterns outside of Sedimentary and Moho Layers.
    \item Upper crust appears to have more consistent structure, though only marginally 4th and 5th principal components
    \item Lower crust appears more heterogenous.
    \item Brittle Ductile transition? See Roy Hynmann
    \item Conrad may be last reflector in an more reflective upper crust, similar to the reflection moho. This interpretation may be more consistent with the dataset
    \item
  \end{itemize}

\item Crustal Evolution
  \begin{itemize}
    \item Archean vs Proterozoic
    \item Canada Averages
    \item Regional Averages
    \item Compare data to Crust 2.0. What do the differences mean.
      \begin{itemize}
      \item Lith 5.0 data?
      \item Lith5.0 (Perry, 2002) estimates for Canadian crustal averages is 38 km. The Crust
        2.0 average is 38 km as well, however this is expected since Crust2.0 data for
        Canada is based on the same data as that of Lith5.0 .... is it definately?

@@

    \item Secular variation in NE Churchill from thinner crusts to thicker as we move East
      \begin{itemize}
      \item in the literature? See Lith 5.0: A revised crustal model for Canada based on lithoprobe results.
      \end{itemize}
  \end{itemize}
